Methodology for Assessing the State of the Practice for Domain X

### 2020-09-27 StateOfPractice/Methodology/Methodology.tex
updated section 2 of Methodology

\section{Research Questions}\label{ResearchQuestions}
	\begin{enumerate} 
		\item What artifacts are recommended for research software development?
\pmi{remove}
		\item What artifacts do current software projects produce?
\pmi{keep}
		\item What artifacts are produced in existing software development processes. 
\pmi{remove}
		\item What information is captured by current projects artifacts?
\pmi{keep}
		\item What information is necessary to capture for sustainability and productivity?
\pmi{need to review - subjective, can we capture this from gathering state of practice data?}
		\item What commonalities exist among software artifacts?
\pmi{keep}
		\item What are sustainable and productive methods to produce softifacts?
\pmi{remove}
		\item What are the consequences of technology tools towards sustainability and productivity  \pmi{keep, reword: what technology tools are used? what do they capture? benefits?}
		\item What are the common factors that lead to sustainability and productivity?
\pmi{need to review, reword. How do we gather sustainability from SOP data?}
		\item What relationships exist, if any, between 'high ranking' software projects and sustainability/productivity?
 \pmi{need to review}	
		\item What skills/knowledge are needed by future developers?	\pmi{copied from original - review}
		\item What are the common pain points?	\pmi{copied from original - review}
		\item How can the development process be improved?	\pmi{copied from original - review}
	\end{enumerate}

>>>>

\section{Research Questions}\label{ResearchQuestions}

Questions from Olu's Research Proposal:
	\begin{enumerate} 
		\item What artifacts are recommended for research software development?
\pmi{remove}
		\item What artifacts do current software projects produce?
\pmi{keep}
\item What information is captured by current software project artifacts?\pmi{keep}
\item What information is necessary to capture for sustainability?\pmi{remove}
\item What information is necessary to capture for productivity?\pmi{remove}
\item What commonalities exist among software artifacts?\pmi{need to review}
\item How can we improve sustainability in research softifacts development practices?\pmi{remove}
\item What are the consequences of technology tools towards sustainability and productivity?\pmi{remove}
\item What are attitudes of research software developers and engineer towards sustainability and productivity with respect to producing softifacts? \pmi{keep}
\item What are the factors that lead to sustainability and productivity?\pmi{remove}
\item What relationships exist between `high rated' software projects and sustainability with respect to research softifacts production? \pmi{remove}
\end{enumerate}

Questions from Overall Research Project folder
\begin{enumerate}
	\item What knowledge is currently captured in the artifacts generated by
	existing open source SCS projects?\pmi{keep}
	\item What principles, processes, methodologies and tools are used by existing open source SCS projects?\pmi{keep}
	\item What are the pain points" for developers working on SCS projects?
	What aspects of the existing processes, methodologies and tools do
	they consider could potentially be improved?\pmi{keep}
	\item For a given software product (softifacts), how can we produce a reasonable measure of the software qualities (correctness, reliability, usability etc.) with a few hours of effort?\pmi{remove}
	\item For a given software product (softifacts), how can we produce a meaningful measure of usability with a few days worth of effort?\pmi{remove}
	\item For a given software product (softifacts), how can we produce a meaningful measure of maintainability (with respect to likely changes) with
	a few days worth of effort?\pmi{remove}
	\item For a given software product (softifacts), how can we produce a meaningful measure of reproducibility/replicability with a few days worth of
	effort?\pmi{remove}
	\item With a reasonable effort and time, how can we compare the productivity between different processes, methodologies and tools?\pmi{remove}
	\item Can a correlation be identified between software projects that use
	best practices for the development process and methodologies and improvement in the qualities of usability, performance and reproducibility/replicability?\pmi{remove}
	\item Ignoring the time and effort required, what knowledge is necessary to
	capture for sustainable SCS? How can this knowledge best be documented in software artifacts?\pmi{remove}
	\item How can Model Driven Engineering and Code Generation be t in the
	development process for SCS to remove as many repetitive, tedious and
	error prone tasks as possible? We will call this the ideal process."\pmi{remove}
	\item How well do existing modelling and code generation tools do at implementing the ideal process"? Candidates for comparison include Drasil
	and Epsilon.\pmi{remove}
	\item How well does a model driven approach to compared to a traditional
	approach for usability, productivity and sustainability?\pmi{remove}
	\item What are the attitudes and preferences of typical users towards an
	implementation of the ideal process"?\pmi{remove}
\end{enumerate}
